Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2020-05-04 PaperMagneticProfiles_JBSMSE.tex
Perform major reorganization.
This is a large commit. Scripts, figures, and datasets were moved to
subdirectories. The README was updated to explain the repo structure.
Include reference to GitHub release in manuscript.
Correct spacing in appendix.
Add reference with curves for dtad.
Correct equation of utilization.
The equation for utilization used the solid specific heat in the numerator,
where the correct is to use the fluid specific heat.
Improve explanation of reduction of blow fraction.

\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field. \cite{bib:trevizoli16_perfor_model}.

@@

\begin{equation}
  \label{eq:110}
  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{s}}{2 f m\ped{s} c\ped{s}}
\end{equation}

@@

Simulations were carried out for various values of blow fraction. The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields. In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.

@@

@@

\bibliography{thermo-ref/Thermo-Foam-Ref,thesis}

>>>>

\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field. \cite{bib:trevizoli16_perfor_model}. Experimental curves of $\dtad$ can be found in \cite{bib:bahl09}.

@@

\begin{equation}
  \label{eq:110}
  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{f}}{2 f m\ped{s} c\ped{s}}
\end{equation}

@@

Simulations were carried out for various values of blow fraction. The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields, thereby increasing the average variation in magnetic field \cite{bib:nakashima18-influen-exp}; this does not happen with the instantaneous profile, since the field is constant and reducing the blow fraction will only reduce the period where the fluid is in contact with the warmed up solid, decreasing the regenerator effectiveness. In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.

@@

\section*{Supplementary Material}
\label{sec:suppl-mater}

The datasets for the results shown in this paper, the source code used to produce the figures and the \LaTeX{} manuscript for this work are available at \cite{bib:fortkamp19-repo-pprof}.

@@

\bibliography{Thermo-Foam-Ref,thesis}
